What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-08-07 manuscript.tex
Render Quarto Manuscript

\abstract{%
We tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based eye-tracking format. Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js. In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment. These studies also varied in the type of eye-tracking display, including screens split into halves (Exps. 3 and 5) or quadrants (Exps. 2 \& 4), or composed scenes with regions of interest that varied in size (Exp. 1). Outcomes were mixed. The least successful replication attempt was Exp. 1; we did not obtain a condition effect in our remote sample (1a), nor in an in-lab follow-up (1b). However, the other four experiments were more successful, replicating a blank-screen effect (Exp. 2), a novelty preference (Exp. 3), a verb bias effect (Exp. 4), and a gaze-bias effect in decision-making. These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution should be adapted to coarser quadrant or split-half displays.
}

@@

An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time). This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research. Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic {[}WEIRD; Henrich, Heine, and Norenzayan (2010){]} convenience samples (but see Ryskin, Salinas, Piantadosi, \& Gibson, 2023), which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.

Advances in software for online data collection (de Leeuw, 2015; Papoutsaki et al., 2016) have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples. In particular, \texttt{Webgazer.js} (Papoutsaki et al., 2016) is a webcam-based Javascript plug-in that works in the browser. It can be integrated with any Javascript web interface. As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as \texttt{jsPsych} (de Leeuw, 2015), \texttt{Gorilla} (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or \texttt{lab.js} (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021). However, the added convenience comes at the cost of spatial and temporal resolution. The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are the subject of the current study.

A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data. In what follows, we provide a brief review of the published work that we are aware of (note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., Bánki, Eccher, Falschlehner, Hoehl, \& Markova, 2022).

Semmelmann and Weigelt (2018) compared eye-tracking results between in-lab (n=29) and online (n=28) studies in three tasks: fixation, pursuit, and free viewing. They used the \texttt{Webgazer.js} library (Papoutsaki et al., 2016) and programmed tasks in HTML/Javascript directly. The first two tasks tested measurement of basic gaze properties. In the fixation task, participants were asked to fixate a dot, and in the pursuit task, they were asked to follow a dot with their eyes. In the free viewing task, the eye movements may have been more semantically driven: participants were shown a picture of a human face and asked to look wherever they wanted to on the image. Webgazer was successful in accurately detecting fixation locations and saccades in all three tasks, though online data (collected through a crowdsourcing platform) were slightly more variable and delayed relative to the in-lab data. The free viewing task replicated previously observed statistical patterns (e.g., more fixations on eyes than mouths).

Similarly, Yang and Krajbich (2021) used the \texttt{Webgazer.js} library (Papoutsaki et al., 2016) combined with the \texttt{jsPsych} library for conducting behavioral experiments in a web browser (de Leeuw, 2015), to replicate a well-established link between value-based decision-making and eye gaze Krajbich, Armel, \& Rangel (2010). Online participants (n=38) first saw a series of images of 70 snack foods and rated how much they liked each one. During the primary task, on each of 100 trials, two of the snack food images were displayed on the left and right sides of the display and participants chose the one that they preferred while their gaze was monitored. As in previous work, participants were biased to choose the option they had spent more time looking at. The authors also implemented a code modification to address temporal delays in \texttt{WebGazer}.

Several papers have used the \texttt{WebGazer.js} library (via different interfaces) to replicate visual world paradigm studies. Slim and Hartsuiker (2022) used the \texttt{PCIbex} online experiment platform (Zehr \& Schwarz, 2018) to replicate a study in which participants (n=90) listened to sentences (e.g., Mary reads a letter) while viewing four pictures displayed across the four quadrants of the screen {[}e.g., a letter, a backpack, a car and a wheelchair; Dijkgraaf, Hartsuiker, and Duyck (2017){]}. When the verb in the sentence was \emph{constraining} (e.g., read) with respect to the display (only the letter would be an appropriate continuation), listeners made more fixations to the target image (letter) than when the verb was \emph{neutral} (e.g., Mary steals a letter), as in previous work. However, they observed a substantial delay of \textasciitilde200ms in the onset of the effect relative to the in-lab study with an infrared eyetracker and a reduction in effect size (despite a threefold increase in sample size relative to the original). The authors noted that delay was particularly problematic given that the purpose of the original study was to capture aspects of predictive or anticipatory processing: in the original study, but not in the web replication, the difference between \emph{constraining} and \emph{neutral} conditions emerged before the onset of the final noun (e.g., letter). Similarly, Degen, Kursat, and Leigh (2021) reported that effects of scalar implicature processing (comparing looks to the target in a four quadrant display for sentences such as ``Click on the girl that has \emph{some} apples'' vs.~``Click on the girl that has \emph{three} apples'' ) were smaller and delayed relative to those observed in the lab (Sun \& Breheny, 2020).

In contrast, using the \texttt{Gorilla} experiment platform (Anwyl-Irvine et al., 2020), Prystauka, Altmann, and Rothman (2023) observed robust effects of verb semantics and lexical interference in similar time windows to previous in-lab studies (Altmann \& Kamide, 1999; Kukona, Cho, Magnuson, \& Tabor, 2014), though a direct comparison was not possible because their studies used different materials than the in-lab experiments they were conceptually replicating. Furthermore, using \texttt{jsPsych}, Vos, Minor, and Ramchand (2022) closely replicated the magnitude and timecourse of effects in a lab-based visual world paradigm where the regions of interest (ROIs) consisted of the left and right halves of the display, suggesting that the concerns about poor temporal resolution can be mitigated. Indeed, the eye-tracking plug-in in \texttt{jsPsych} uses a fork of \texttt{Webgazer.js} in which certain modifications have been made to minimize processing time. \footnote{See discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}}

Finally, Van der Cruyssen et al. (2023) used \texttt{WebGazer.js} in conjunction with \texttt{PsychoJS} to conceptually replicate three paradigms, one which is analogous to Yang and Krajbich (2021), another testing the novelty preference (tendency for learners to look more at an object that they have not yet studied), and a visual world paradigm study with 4 objects, similar to Prystauka et al. (2023). These replications were successful but they noted reductions in effect sizes relative to an in-lab dataset. They did not address whether there were temporal delays.

In sum, webcam eye-tracking has been used to varying degrees of success across a small set of paradigms that are used in cognitive science research. One configuration, \texttt{jsPsych} with a modification of \texttt{WebGazer.js}, appears to have circumvented initial limitations in temporal precision (Krajbich et al., 2010; Vos et al., 2022) but has only been tested with paradigms with minimal requirements in terms of spatial precision (both experiments used the two sides of the display as the ROIs). Further, the extent to which noise in the measurement is due to the software and hardware limitations as opposed to the difference between the in-lab and online settings remains unclear. In the current work, we evaluate a broad variety of paradigms in terms of their suitability for webcam eye-tracking in order to provide guidance for cognitive scientists aiming to increase and diversify participation in their eye-tracking-based research.

@@

We used R (Version 4.4.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.3; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.

@@

Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking. In the remote sample, results were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance; the one exception was in comparing first target fixation latencies across verb conditions, but only when aggressive exclusion criteria were applied to participants (INSERT WHAT THOSE CRITERIA WERE). To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting. Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically.

Taken together, the instability of these effects might suggest that this paradigm is not well-suited for web-based eye-tracking. Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration. The next four experiments test paradigms with more generous ROIs.

@@

The fifth study was a replication attempt of Shimojo et al. (2003),
which found that human gaze is actively involved in preference
formation. Separate sets of participants were shown pairs of human faces
and asked either to choose which one they found more attractive or which
they felt was rounder. Prior to making their explicit selection,
participants were increasingly likely to be fixating the face they
ultimately chose, though this effect was significantly weaker for
roundness discrimination.

@@

Experiment 4 used the four quadrants of the participant's screen as ROIs. As in Ryskin et al. (2017), listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input (``Rub the frog with the mitten''). Across multiple time windows, participants looked more at potential instruments (mitten), when the verb (rub) was one that was more likely to be followed by a prepositional phrase describing an instrument with which to perform the action , as opposed to describing the recipient of the action (frog). Despite the qualitative replication of past findings, the overall rates of looks to various objects were much lower than in an in-lab study using infrared eye-tracking. This reduction may be related to measurement quality: effect sizes were greater for participants with higher calibration accuracy. Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect. Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to \texttt{webgazer} that are made within the \texttt{jsPsych} plug-in successfully address the issues noted by Dijkgraaf et al. (2017) and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.

@@

\bibitem[\citeproctext]{ref-banki2022comparing}
Bánki, A., Eccher, M. de, Falschlehner, L., Hoehl, S., \& Markova, G. (2022). Comparing online webcam-and laboratory-based eye-tracking for the assessment of infants' audio-visual synchrony perception. \emph{Frontiers in Psychology}, \emph{12}, 733933.

@@

@@

@@

@@

\bibitem[\citeproctext]{ref-krajbich2010visual}
Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.

\bibitem[\citeproctext]{ref-kukona2014lexical}
Kukona, A., Cho, P. W., Magnuson, J. S., \& Tabor, W. (2014). Lexical interference effects in sentence processing: Evidence from the visual world paradigm and self-organizing models. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 326.

@@

@@

@@

@@

@@

@@

@@

\bibitem[\citeproctext]{ref-sun2020another}
Sun, C., \& Breheny, R. (2020). Another look at the online processing of scalar inferences: An investigation of conflicting findings from visual-world eye-tracking studies. \emph{Language, Cognition and Neuroscience}, \emph{35}(8), 949--979.

@@

\bibitem[\citeproctext]{ref-zehr2018PCIbex}
Zehr, J., \& Schwarz, F. (2018). \emph{PennController for internet based experiments (IBEX)}. Retrieved from \url{https://doi.org/10.17605/OSF.IO/MD832}

>>>>

\abstract{%
We tested whether the results of five different eye-tracking experiments in the cognitive psychology literature would replicate in a webcam-based eye-tracking format. Specifically, we carried out five experiments by integrating two javascript-based tools: js.psych and a modified version of Webgazer.js. In order to represent a wide range of applications of eye-tracking to cognitive psychology, we chose two psycholinguistic experiments, two memory experiments, and a decision-making experiment. These studies also varied in the type of eye-tracking display, including screens split into halves (Exps. 3 and 5) or quadrants (Exps. 2 \& 4), or composed scenes with regions of interest that varied in size (Exp. 1). Outcomes were mixed. The least successful replication attempt was Exp. 1; we did not obtain a condition effect in our remote sample (1a), nor in an in-lab follow-up (1b). However, the other four experiments were more successful, replicating a blank-screen effect (Exp. 2), a novelty preference (Exp. 3), a verb bias effect (Exp. 4), and a gaze-bias effect in decision-making (Exp. 5). These results suggest that webcam-based eye tracking can be used to detect a variety of cognitive phenomena, including those with sensitive time, although paradigms that require high spatial resolution should be adapted to coarser quadrant or split-half displays.
}

@@

An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time). This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research. Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic {[}WEIRD; Henrich, Heine, and Norenzayan (2010){]} convenience samples (but see Ryskin, Salinas, Piantadosi, \& Gibson, 2023), which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition. Likewise, the sample sizes for in-lab experiments are usually orders of magnitude smaller than what statisticians recommend (Nosek et al., 2022).

A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants (Gosling, Sandy, John, \& Potter, 2010; Hartshorne, Leeuw, Goodman, Jennings, \& O'Donnell, 2019; Li, Germine, Mehr, Srinivasan, \& Hartshorne, 2024; Reinecke \& Gajos, 2015). Historically, this option has not been available for eye-tracking. This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking (e.g., Snedeker \& Trueswell, 2003). Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic. In recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy (Burton, Albert, \& Flynn, 2014; Papoutsaki et al., 2016; Skovsgaard, Agustin, Johansen, Hansen, \& Tall, 2011; Zheng \& Usagawa, 2018). However, webcam-based eyetracking only started to be used regularly in research with the advent of \texttt{Webgazer.js} (Papoutsaki et al., 2016), a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including \texttt{jsPsych} (de Leeuw, 2015), \texttt{Gorilla} (Anwyl-Irvine, Massonnié, Flitton, Kirkham, \& Evershed, 2020), or \texttt{lab.js} (Henninger, Shevchenko, Mertens, Kieslich, \& Hilbig, 2021).

Given the potential game-changing nature of webcam-based eye-tracking, a number of research groups have investigated how well it works. There are two potential limitations to webcam-based eye-tracking. First, the spatial and temporal resolution is less than what is achievable with an infrared system. Second, testing subjects over the Internet involves less control: subjects may be unable or unwilling to calibrate equipment, adjust lighting, etc., to the same level of precision typical of in-lab studies. Nearly all this work has used \texttt{Webgazer.js} --- most in combination with jsPsych, but some with Gorilla or hand-built integrations.

Results to date have been encouraging. Semmelmann and Weigelt (2018) found data quality was reasonable for fixation location and saccades in fixation, smooth pursuit, and free-viewing tasks, though data collected online through a crowdsourcing platform was slightly more variable and timing was somewhat delayed compared to data collected in the lab. Several researchers successfully replicated well-known findings from the sentence-processing literature involving predictive looks (Degen, Kursat, \& Leigh, 2021; Prystauka, Altmann, \& Rothman, 2023; Van der Cruyssen et al., 2023; Vos, Minor, \& Ramchand, 2022). Yang and Krajbich (2021) successfully replicated a well-established link between value-based decision-making and eye gaze (see also Van der Cruyssen et al., 2023).

While promising, there are some salient limitations. First, many of the studies report effects that are smaller or later than what had been previously observed in the lab (Degen et al., 2021; Slim \& Hartsuiker, 2022; Van der Cruyssen et al., 2023). Importantly, accurate timing on a web browser is not trivial (De Leeuw \& Motz, 2016; Passell et al., 2021), and subtle programming choices can significantly affect the accuracy of \texttt{WebGazer.js} timing (Yang \& Krajbich, 2021).\footnote{See also discussion at \url{https://github.com/jspsych/jsPsych/discussions/1892}} Since most of the prior work did not address these timing issues, it is not clear how many of the reported lab/web differences would resolve.

Second, prior work has focused on studies with relatively coarse-grained regions of interest (but see Semmelmann \& Weigelt, 2018), dividing the screen either in half or in quadrants. This is particularly salient with (Prystauka et al., 2023), which simplified (Altmann \& Kamide, 1999)'s design so that regions of interest are quadrants rather than the finer-grained ROIs used in the original. Certainly, webcam eyetracking will not be as spatially fine-grained as an infrared eyetracker, but we do not yet have a good sense of the limits.

Finally, the prior work has focused on a relatively limited range of methods. Different paradigms have different technical requirements and analyze the results differently. As a result, the breadth of utility of webcam eye-tracking is unclear.

@@

We used R (Version 4.4.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.5; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.

@@

Overall, the results of Experiment 1 paint a sobering picture of web-based eye-tracking. In the remote sample, results were in the expected direction but effects were smaller and delayed relative to previous work and failed to reach statistical significance; the one exception was in comparing first target fixation latencies across verb conditions, but only when aggressive exclusion criteria were applied to participants (INSERT WHAT THOSE CRITERIA WERE). To test whether this could be explained by the variability in experimental settings across participants, we replicated our procedure in a lab setting. Surprisingly, the results in the in-lab study were less aligned with previous work; critical effects were not significant nor were they in the expected direction numerically. This suggests the problem was not with running the study online or due to working with a more diverse population.

Taken together, the instability of these effects might suggest that this paradigm is not well-suited for webcam-based eye-tracking. Notably, the ROIs were tightly drawn around the five to six objects in each scene (larger ROIs would have led to overlapping objects) and thus, analyses were unforgiving of inaccurate calibration. Further evidence comes from (Prystauka et al., 2023), who ran a modified version of the Altmann and Kamide study with only 4 objects, allowing larger, more distinct ROIs.

The next four experiments test paradigms with more generous ROIs.

@@

The fifth study was a replication attempt of Shimojo, Simion, Shimojo, and Scheier (2003),
which found that human gaze is actively involved in preference
formation. Separate sets of participants were shown pairs of human faces
and asked either to choose which one they found more attractive or which
they felt was rounder. Prior to making their explicit selection,
participants were increasingly likely to be fixating the face they
ultimately chose, though this effect was significantly weaker for
roundness discrimination.

@@

Experiment 4 used the four quadrants of the participant's screen as ROIs. As in Ryskin et al. (2017), listeners used knowledge of the co-occurrence statistics of verbs and syntactic structures to resolve ambiguous linguistic input (``Rub the frog with the mitten''). Across multiple time windows, participants looked more at potential instruments (mitten), when the verb (rub) was one that was more likely to be followed by a prepositional phrase describing an instrument with which to perform the action , as opposed to describing the recipient of the action (frog). Despite the qualitative replication of past findings, the overall rates of looks to various objects were much lower than in an in-lab study using infrared eye-tracking. This reduction may be related to measurement quality: effect sizes were greater for participants with higher calibration accuracy. Using the full quadrants as ROIs, rather than bounding boxes around the four images, also appeared to improve the measurement of the effect. Crucially, there was no evidence of a delay in the onset of effects relative to in-lab work, indicating that the modifications to \texttt{webgazer} that are made within the \texttt{jsPsych} plug-in successfully address the issues noted by Dijkgraaf, Hartsuiker, and Duyck (2017) and suggesting that this methodology can be fruitfully used to investigate research questions related to the timecourse of processing.

@@

@@

\bibitem[\citeproctext]{ref-burton2014comparison}
Burton, L., Albert, W., \& Flynn, M. (2014). A comparison of the performance of webcam vs. Infrared eye tracking technology. \emph{Proceedings of the Human Factors and Ergonomics Society Annual Meeting}, \emph{58}, 1437--1441. SAGE Publications Sage CA: Los Angeles, CA.

@@

\bibitem[\citeproctext]{ref-de2016psychophysics}
De Leeuw, J. R., \& Motz, B. A. (2016). Psychophysics in a web browser? Comparing response times collected with JavaScript and psychophysics toolbox in a visual search task. \emph{Behavior Research Methods}, \emph{48}, 1--12.

@@

\bibitem[\citeproctext]{ref-gosling2010wired}
Gosling, S. D., Sandy, C. J., John, O. P., \& Potter, J. (2010). Wired but not WEIRD: The promise of the internet in reaching more diverse samples. \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 94.

\bibitem[\citeproctext]{ref-hartshorne2019thousand}
Hartshorne, J. K., Leeuw, J. R. de, Goodman, N. D., Jennings, M., \& O'Donnell, T. J. (2019). A thousand studies for the price of one: Accelerating psychological science with pushkin. \emph{Behavior Research Methods}, \emph{51}, 1782--1803.

@@

@@

\bibitem[\citeproctext]{ref-li2024developmental}
Li, W., Germine, L. T., Mehr, S. A., Srinivasan, M., \& Hartshorne, J. (2024). Developmental psychologists should adopt citizen science to improve generalization and reproducibility. \emph{Infant and Child Development}, \emph{33}(1), e2348.

@@

\bibitem[\citeproctext]{ref-nosek2022replicability}
Nosek, B. A., Hardwicke, T. E., Moshontz, H., Allard, A., Corker, K. S., Dreber, A., et al.others. (2022). Replicability, robustness, and reproducibility in psychological science. \emph{Annual Review of Psychology}, \emph{73}, 719--748.

@@

\bibitem[\citeproctext]{ref-passell2021cognitive}
Passell, E., Strong, R. W., Rutter, L. A., Kim, H., Scheuer, L., Martini, P., \ldots{} Germine, L. (2021). Cognitive test scores vary with choice of personal digital device. \emph{Behavior Research Methods}, \emph{53}(6), 2544--2557.

@@

\bibitem[\citeproctext]{ref-reinecke2015labinthewild}
Reinecke, K., \& Gajos, K. Z. (2015). LabintheWild: Conducting large-scale online experiments with uncompensated samples. \emph{Proceedings of the 18th ACM Conference on Computer Supported Cooperative Work \& Social Computing}, 1364--1378.

@@

\bibitem[\citeproctext]{ref-skovsgaard2011evaluation}
Skovsgaard, H., Agustin, J. S., Johansen, S. A., Hansen, J. P., \& Tall, M. (2011). Evaluation of a remote webcam-based eye tracker. \emph{Proceedings of the 1st Conference on Novel Gaze-Controlled Applications}, 1--4.

@@

\bibitem[\citeproctext]{ref-snedeker2003using}
Snedeker, J., \& Trueswell, J. (2003). Using prosody to avoid ambiguity: Effects of speaker awareness and referential context. \emph{Journal of Memory and Language}, \emph{48}(1), 103--130.

@@

@@

\bibitem[\citeproctext]{ref-zheng2018rapid}
Zheng, C., \& Usagawa, T. (2018). A rapid webcam-based eye tracking method for human computer interaction. \emph{2018 International Conference on Control, Automation and Information Sciences (ICCAIS)}, 133--136. IEEE.
